RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-09-17 doc/paper.tex
update

An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by LS procedure. At each iteration, ILS applies three steps. First, the current incumbent solution is perturbed, that is mutated. The perturbed solution is then improved by LS procedure. The outcome is thereafter compared to the incumbent solution and possibly replaced for the new one, with accordance to the chosen acceptance criterion.

>>>>

An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by LS procedure. At each iteration, ILS applies three steps. First, the current incumbent solution is perturbed, that is mutated. Secondly, the perturbed solution is then improved by LS procedure. Thirdly, the LS outcome is thereafter compared to the incumbent solution and possibly replaced as the new one, with accordance to the chosen acceptance criterion.
